---
title: IHDP analyses for Ch. 19 of GHV book
output:
    html_document:
        toc: true
        toc_float: true
        theme: lumen
        highlight: zenburn
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(include=TRUE)
knitr::opts_chunk$set(message=FALSE)
knitr::opts_chunk$set(warning=FALSE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
knitr::opts_knit$set(root.dir='..')
```

```{r library functions}
library(dbarts)
library(rstan)
    options(mc.cores=parallel::detectCores())
library(rstanarm)
library(arm)
source('code/matching.R')
source('code/balance.R')
source('code/estimation.R')
```


# Reading in the data
Loading the data like this will create a dataframe called cc2.  It will be helpful later if we choose indicator versions of categorical variables and if we create separate indices for binary and continuous variables, so we'll create those now.
```{r data}
load("data/cc2.Rdata")
trt <- cc2$treat==1
```


# Step 1: Picking confounders {.tabset .tabset-fade}

- income is technically post treatment
- st99 also problematic since only appears in the control group

```{r}
covs.bin <- c("bwg","hispanic","black","white","b.marr","lths","hs","ltcoll","college","work.dur","prenatal","sex","first","st5","st9","st12","st25","st36","st42","st48","st53")
# above is good for balance checks but will lead to linear dependencies to avoid use this version (nr = no redundancy)
covs.bin.nr <- c("bwg","hispanic","black","b.marr","lths","hs","ltcoll","work.dur","prenatal","sex","first","st5","st9","st12","st25","st36","st42","st48","st53")
covs.cont <- c("bw","preterm","momage","dayskidh")
```

## Initial set
```{r}
covs <- c(covs.cont, covs.bin)
print(covs)
```

## No redundancy
```{r}
covs.nr <- c(covs.cont, covs.bin.nr)
print(covs.nr)
```


# Step 2: Propensity score estimation {.tabset .tabset-fade}

## Initial set
```{r}
form0 <- as.formula(cc2[, c("treat", covs)])
# stan
ps_fit_0 <- stan_glm(form0, family=binomial(link='logit'), data=cc2, algorithm='optimizing')
pscores0 <- apply(posterior_linpred(ps_fit_0, type='link'), 2, mean)
# base
ps_fit_0b <- glm(form0, family=binomial(link='logit'), data=cc2)
pscores0b <- predict(ps_fit_0b, type='link')

cor(pscores0, pscores0b)
```

## No redundancy
```{r}
form1 <- as.formula(cc2[, c("treat", covs.nr)])
# stan
ps_fit_1 <- stan_glm(form1, family=binomial(link='logit'), data=cc2, algorithm='optimizing')
pscores1 <- apply(posterior_linpred(ps_fit_1, type='link'), 2, mean)
# base
ps_fit_1b <- glm(form1, family=binomial(link='logit'), data=cc2)
pscores1b <- predict(ps_fit_1b, type='link')

cor(pscores1, pscores1b)
```


# Step 3: Use the propensity score to match {.tabset .tabset-fade}

## Initial set
```{r}
# w/o replacement
matches0 <- matching(z=cc2$treat, score=pscores0, replace=FALSE)
matches0b <- matching(z=cc2$treat, score=pscores0b, replace=FALSE)

# w/ replacement
matches0.wr <- matching(z=cc2$treat, score=pscores0, replace=TRUE)
matches0b.wr <- matching(z=cc2$treat, score=pscores0b, replace=TRUE)
```

## No redundancy
```{r}
# w/o replacement
matches1 <- matching(z=cc2$treat, score=pscores1, replace=FALSE)
matches1b <- matching(z=cc2$treat, score=pscores1b, replace=FALSE)

# w/ replacement
matches1.wr <- matching(z=cc2$treat, score=pscores1, replace=TRUE)
matches1b.wr <- matching(z=cc2$treat, score=pscores1b, replace=TRUE)
```


# Step 4: Checking balance and overlap {.tabset .tabset-fade}

## Initial set

**Balance**
```{r}
# w/o replacemennt
par(mfrow=c(1,1))
bal0 <- balance(rawdata=cc2[,covs], cc2$treat, matched=matches0$cnts, estimand="ATT")
plot(bal0)
bal0b <- balance(rawdata=cc2[,covs], cc2$treat, matched=matches0b$cnts, estimand="ATT")
plot(bal0b)

# w/ replacement
bal0.wr <- balance(rawdata=cc2[,covs],treat=cc2$treat,matched=matches0.wr$cnts,estimand="ATT")
plot(bal0.wr)
bal0b.wr <- balance(rawdata=cc2[,covs],cc2$treat,matched=matches0b.wr$cnts,estimand="ATT")
plot(bal0b.wr)
```

**Overlap**
```{r}
# Plot the overlapping histograms for pscore0b, density
hist(pscores0b[cc2$treat==0],
    xlim=c(-67,10), ylim=c(0,.22),
     main="", border="darkgrey", breaks=seq(-67,10,by=1),
     mgp=c(2,.5,0), xlab="propensity scores",freq=FALSE)
hist(pscores0b[cc2$treat==1], freq=FALSE, add=TRUE)

# Plot the overlapping histograms for pscore0b, frequency
hist(pscores0b[cc2$treat==0],
    xlim=c(-67,10), ylim=c(0,300),
     main="", border="darkgrey", breaks=seq(-67,10,by=1),
     mgp=c(2,.5,0), xlab="propensity scores",freq=TRUE)
hist(pscores0b[cc2$treat==1], freq=TRUE, add=TRUE)
```

## No redundancy

**Balance**
```{r}
# w/o replacemennt
par(mfrow=c(1,1))
bal1 <- balance(rawdata=cc2[,covs.nr], cc2$treat, matched=matches1$cnts, estimand="ATT")
plot(bal0)
bal1b <- balance(rawdata=cc2[,covs.nr], cc2$treat, matched=matches1b$cnts, estimand="ATT")
plot(bal1b)

# w/ replacement
bal1.wr <- balance(rawdata=cc2[,covs.nr], treat=cc2$treat, matched=matches1.wr$cnts, estimand="ATT")
plot(bal0.wr)
bal1b.wr <- balance(rawdata=cc2[,covs.nr], cc2$treat, matched=matches1b.wr$cnts, estimand="ATT")
plot(bal1b.wr)
```

**Overlap**
```{r}
# Plot the overlapping histograms for pscore1b, density
hist(pscores1b[cc2$treat==0],
    xlim=c(-67,10), ylim=c(0,.22),
     main="", border="darkgrey", breaks=seq(-67,10,by=1),
     mgp=c(2,.5,0), xlab="propensity scores",freq=FALSE)
hist(pscores1b[cc2$treat==1], freq=FALSE, add=TRUE)

# Plot the overlapping histograms for pscore1b, frequency
hist(pscores1b[cc2$treat==0],
    xlim=c(-67,10), ylim=c(0,300),
     main="", border="darkgrey", breaks=seq(-67,10,by=1),
     mgp=c(2,.5,0), xlab="propensity scores",freq=TRUE)
hist(pscores1b[cc2$treat==1], freq=TRUE, add=TRUE)
```


# Step 5: Estimate the treatment effect on re-structured data {.tabset .tabset-fade}
