---
title; IHDP analyses for Ch. 19 of GHV book
output:
    html_document:
        toc: true
        toc_float: true
        theme: lumen
        highlight: zenburn
        df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
knitr::opts_chunk$set(include=TRUE)
knitr::opts_chunk$set(message=TRUE)
knitr::opts_chunk$set(warning=TRUE)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=80), tidy=TRUE)
knitr::opts_knit$set(root.dir='..')
```

```{r functions}
library(rstan)
    options(mc.cores=parallel::detectCores())
library(rstanarm)
library(arm)
source('code/matching.R')
source('code/balance.R')
source('code/estimation.R')
```

# Reading in the data
Loading the data like this will create a dataframe called cc2.  It will be helpful later if we choose indicator versions of categorical variables and if we create separate indices for binary and continuous variables, so we'll create those now.

```{r data}
load("data/cc2.Rdata")
covs.bin <- c("bwg","hispanic","black","white","b.marr","lths","hs","ltcoll","college","work.dur","prenatal","sex","first","st5","st9","st12","st25","st36","st42","st48","st53")
# above is good for balance checks but will lead to linear dependencies to avoid use this version (nr = no redundancy)

covs.bin.nr <- c("bwg","hispanic","black","b.marr","lths","hs","ltcoll","work.dur","prenatal","sex","first","st5","st9","st12","st25","st36","st42","st48","st53")

covs.cont <- c("bw","preterm","momage","dayskidh")

covs <- c(covs.cont, covs.bin)
cov.nms <- c("birth weight","weeks preterm","age at birth","days in hospital","male","first born","age","black","Hispanic","white","unmarried at birth","less than high school","high school graduate","some college","college graduate","worked during pregnancy","had no prenatal care")

covs.nr <- c(covs.cont, covs.bin.nr)
form.bal <- as.formula(cc2[, c("treat", rev(covs))])
mod.for.bal <- glm(form=form.bal, family="binomial", data=cc2)
# income is technically post treatment
# st99 also problematic since only appears in the control group

trtd <- cc2$treat==1
ctrl <- cc2$treat==0
```

# Section 19.5

## Figure 19.9
The first figure in 19.5 (Figure 19.9) shows balance we will return to this after we have performed matching later.

## Figure 19.10
Figure 19.10 displays a scatter plot of birthweight versus test scores at age 3 with observations displayed in different colors.  Postscript commands have been commented out but provide an example of how to output this plot to a postscript file.  The "dev.off" command commented out at the end of the code would also be necessary if the goal is to route the plot to a file.  We exclude this code from the rest of the examples.

```{r fig 19.10}
par(mfrow=c(1,1))
tmp <- lm(ppvtr.36~bw+treat, data=cc2)$coef
plot(cc2$bw, cc2$ppvtr.36, xlab="birth weight", ylab="test score at age 3", mgp=c(2,.5,0), main="", type="n", xlim=c(1500,5000), cex.axis=.75, cex.lab=.8, lab=c(3,5,7), xaxt="n")
axis(side=1, at=c(2000,3000,4000,5000), cex.axis=.75)
points(cc2$bw[ctrl] + runif(sum(ctrl),-.5,5), cc2$ppvtr.36[ctrl], col="darkgrey", pch=20, cex=.3)
points(cc2$bw[trtd] +  runif(sum(trtd),-.5,5), cc2$ppvtr.36[trtd], pch=20, cex=.3)
curve(tmp[1] + tmp[2] * x, add=TRUE, lty=2)
curve(tmp[1] + tmp[3] + tmp[2] * x, add=TRUE)
```

## Figure 19.11
The two plots in Figure 19.11 display overlap across treatment and control groups for two covariates: mother's education and age of child.
*Note to self:* maybe be worth dropping age of child since it's hard to explain.

```{r fig 19.11}
par(mfrow=c(1,2))
hist(cc2$educ[ctrl],
    xlim=c(0,5), main="", border="darkgrey", breaks=c(.5,1.5,2.5,3.5,4.5), mgp=c(2,.5,0), xlab="mother's education", freq=FALSE)
hist(cc2$educ[trtd],
    xlim=c(0,5), xlab="education", breaks=c(.5,1.5,2.5,3.5,4.5), freq=FALSE, add=TRUE)
#
hist(cc2$age[ctrl],
    xlim=c(0,110), main="", xlab="age of child (months)", border="darkgrey", breaks=seq(0,110,10), mgp=c(2,.5,0), ylim=c(0,.1),
     freq=FALSE)
hist(cc2$age[trtd],
    xlim=c(0,110), xlab="", breaks=seq(0,110,10), freq=FALSE, add=T)

par(mfrow=c(1,2))
hist(cc2$preterm[ctrl],
    main="", xlab="preterm", border="darkgrey", mgp=c(2,.5,0), freq=FALSE, breaks=seq(-8,14,1))
hist(cc2$preterm[trtd],
    main="", xlab="preterm", freq=FALSE, add=TRUE)
#
hist(cc2$dayskidh[ctrl],
    main="", xlab="days in hospital", border="darkgrey", mgp=c(2,.5,0),freq=FALSE, breaks=seq(0,100,5))
hist(cc2$dayskidh[trtd],
    main="", xlab="preterm", freq=FALSE, add=TRUE)
```
These last two might be the more interesting to include in the manuscript.


# Section 19.6

Section 19.6 starts with a table presenting results from a stratified analysis of the effect of the IHDP treatment broken down by mother's education.

```{r stratified analysis}
treatment_ppvtr36 <- apply(cc2[trtd, c('lths', 'hs', 'ltcoll', 'college')], MARGIN=2, FUN=function(edu, post=cc2$ppvtr36) {mean(post[edu==1])})
treatment_sizes <- apply(cc2[trtd, c('lths', 'hs', 'ltcoll', 'college')], MARGIN=2, FUN='sum')
control_sizes <- apply(cc2[ctrl, c('lths', 'hs', 'ltcoll', 'college')], MARGIN=2, FUN='sum')
std_errors <- apply(cc2[, c('lths', 'hs', 'ltcoll', 'college')], MARGIN=2, FUN=function(x) {
    sqrt(
        var(x[trtd &])
    )
})

tes.ns <- matrix(0,4,4)
tes.ns[1,] <- c(mean(cc2$ppvtr.36[cc2$treat==1 & cc2$lths==1]) - mean(cc2$ppvtr.36[cc2$treat==0 & cc2$lths==1]), 
                sum(cc2$treat==1 & cc2$lths==1),
                sum(cc2$lths==1),
                sqrt(
                    var(cc2$ppvtr.36[cc2$treat==1 & cc2$lths==1]) / sum(cc2$treat==1 & cc2$lths==1) + var(cc2$ppvtr.36[cc2$treat==0 & cc2$lths==1]) / sum(cc2$treat==0 & cc2$lths==1)
                    )
                )
tes.ns[2,] <- c(mean(cc2$ppvtr.36[cc2$treat==1 & cc2$hs==1]) - mean(cc2$ppvtr.36[cc2$treat==0 & cc2$hs==1]),
                sum(cc2$treat==1 & cc2$hs==1),
                sum(cc2$hs==1),
                sqrt(
                    var(cc2$ppvtr.36[cc2$treat==1 & cc2$hs==1]) / sum(cc2$treat==1 & cc2$hs==1) + var(cc2$ppvtr.36[cc2$treat==0 & cc2$hs==1]) / sum(cc2$treat==0 & cc2$hs==1)
                    )
                )
tes.ns[3,] <- c(mean(cc2$ppvtr.36[cc2$treat==1 & cc2$ltcoll==1]) - mean(cc2$ppvtr.36[cc2$treat==0 & cc2$ltcoll==1]),
                sum(cc2$treat==1 & cc2$ltcoll==1), sum(cc2$ltcoll==1),
                sqrt(
                    var(cc2$ppvtr.36[cc2$treat==1 & cc2$ltcoll==1]) / sum(cc2$treat==1 & cc2$ltcoll==1) + var(cc2$ppvtr.36[cc2$treat==0 & cc2$ltcoll==1]) / sum(cc2$treat==0 & cc2$ltcoll==1)
                    )
                )
tes.ns[4,] <- c(mean(cc2$ppvtr.36[cc2$treat==1 & cc2$college==1]) - mean(cc2$ppvtr.36[cc2$treat==0 & cc2$college==1]),
                sum(cc2$treat==1 & cc2$college==1),
                sum(cc2$college==1),
                sqrt(
                    var(cc2$ppvtr.36[cc2$treat==1 & cc2$college==1]) / sum(cc2$treat==1 & cc2$college==1) + var(cc2$ppvtr.36[cc2$treat==0 & cc2$college==1]) / sum(cc2$treat==0 & cc2$college==1)
                    )
                )

rownames(tes.ns) <- c('lths', 'hs', 'ltcoll', 'college')
colnames(tes.ns) <- c('te', 'n.trt', 'n.ctrl', 'se')
round(tes.ns,2)
```


# Section 19.7: Initial propensity score analysis
The most basic model includes all covariates without transformations or interactions.

```{r}
print(covs)
form0 <- as.formula(cc2[, c('treat', covs)])

ps_fit_0 <- stan_glm(form0, family=binomial(link='logit'), data=cc2, algorithm='optimizing')
pscores0 <- apply(posterior_linpred(ps_fit_0, type='link'), MARGIN=2, FUN=mean)
```

## Step 3: Use propensity score to match
First we will try generating one-to-one matches without replacement. The advantage of this is that we can use the output to create a new dataset that maintains all the matched units.  Since every observation is used only once we can simply run subsequent diagnostics and analyses on this matched dataset.

```{r mwor}
matches0 <- matching(z=cc2$treat, score=pscores0, replace=FALSE)
```

We may prefer however to use matching with replacement in an attempt to maximize the number of good matches.  This time we'll set the option replace to equal TRUE.  The output now will include a variable named "cnts" that we will use in subsequent analyses to reflect the pseudo-population that this matching procedures has created.

```{r mwr}
matches0.wr <- matching(z=cc2$treat, score=pscores0, replace=TRUE)
```

## Step 4: Checking balance and overlap

### Step 4a: Checking balance
Lets check balance and overlap on the matched data.  One option is the plot in Figure XXX.  [THIS SHOULD USE THE MATCHED DATA FROM THE PREFERRED MODEL THAT WE DETERMINE LATER]  That can be produced using the following code:

```{r balance wor}
par(mfrow=c(1,1))
bal0 = balance(rawdata=cc2[,covs], cc2$treat, matched=matches0$cnts,estimand="ATT")
plot(bal0)
# bayesian pscores def work better here
sum(bal0$diff.means.matched[,4])
```

Now let's see what this looks like for matching with replacement (this plot does not appear in the chapter).

```{r balance wr}
bal0.wr <- balance(rawdata=cc2[,covs], treat=cc2$treat, matched=matches0.wr$cnts, estimand="ATT")
plot(bal0.wr)
sum(bal0.wr$diff.means.matches[,4])
```

## DOES IT MAKE SENSE AT THIS POINT TO COMPARE BALANCE BETWEEN THE MATCHING METHODS AND THE ESTIMATION METHODS??

## SOMEWHERE TALK ABOUT HOW THE STANDARDIZATION DIFFERS DEPENDING ON THE ESTIMAND

While in general we prefer visual summaries of our data, including for model fit and diagnostics, one downside to this display is that it displays standardized differences in means for binary variables which may not be the best option.  Since the variance of a binary variable is a function of the mean this means that these differences in means across groups are being standardized differentially based on how close the mean in each group is to .5, which does not seem appropriate.  For this reason common advice is to examine different balance diagnostics for continuous and binary variables.

We demonstrate this using a plot of the data restructured using the matching with replacement approach.

```{r balance binary vs continuous}
# binary
plot(bal0.wr, which.covs="binary")
# continuous
plot(bal0.wr, which.covs="cont")
```

If we want to keep the scale the same as the previous plots then we could use the followinng

```{r balance binary vs continuous 2}
# first plot the binary
plot(bal0.wr, which.covs="binary", x.max=4)
# now plot the continuous
plot(bal0.wr, which.covs="cont", x.max=4)
```

### Step 4b: Checking overlap

First show overlap with our working model

```{r overlap 1}
# Plot the overlapping histograms for pscore0, density
hist(pscores0[cc2$treat==0],
    xlim=c(-41,8), ylim=c(0,.22),
    main="", border="darkgrey", breaks=seq(-41,8,by=1),
    mgp=c(2,.5,0), xlab="propensity scores",freq=FALSE)
hist(pscores0[cc2$treat==1], freq=FALSE, add=TRUE)

# Plot the overlapping histograms for pscore0, frequency
hist(pscores0[cc2$treat==0],
    xlim=c(-41,8), ylim=c(0,450),
    main="", border="darkgrey", breaks=seq(-41,8,by=1),
    mgp=c(2,.5,0), xlab="propensity scores",freq=TRUE)
hist(pscores0[cc2$treat==1], freq=TRUE, add=TRUE)
```
